Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
explain the two first costs

The cost of evaluating a Triple Pattern Fragment plan $C_{tpf}$ is estimated to
be 
\begin{equation}
C_{tpf} = 10 + \floor{990 \frac{n_{tpf}}{n_{tot}}} ,
\end{equation}
where $n_{tpf}$ is the estimated number of triples expected to be
matched by the triple pattern and $n_{tot}$ is the size of the
model. Thus, this cost will be an integer between 10 and 1000. The
reason we use a floor function is that the Attean cost model only
supports integers.

The cost of accessing the cache is assumed to be small compared to the
above, and is estimated as 
\begin{equation}
C_c = 2 + \floor{\log_{10}{n_c}} , 
\end{equation}
where $n_c$ is the number of triples in the cache that matches the
given triple pattern.

>>>>

The cost of evaluating a Triple Pattern Fragment plan $C_{tpf}$ is
designated to be
\begin{equation}
C_{tpf} = 10 + \floor{990 \frac{n_{tpf}}{n_{tot}}} ,
\end{equation}
where $n_{tpf}$ is the estimated number of triples expected to be
matched by the triple pattern and $n_{tot}$ is the size of the
model. Thus, this cost will be an integer between 10 and 1000. The
reason we use a floor function is that the Attean cost model only
supports integers. This choice is mainly motivated from the assumption
that evaluating TPFs is a relatively cheap operation for the remote
endpoint, and so the cost should be contained within an interval, so
that other costs can easily be balanced against it.

It is then assumed that the cost of accessing the cache is usually
lower than the above, i.e. it should usually be below the lowest cost
of a TPF (yet have no upper bound), and is therefore designated as
\begin{equation}
C_c = 2 + \floor{\log_{10}{n_c}} , 
\end{equation}
where $n_c$ is the number of triples in the cache that matches the
given triple pattern.
